Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-05-02 overleaf/results.tex
More cuts... Still 1/2 page over.

\subsection{Benchmarks}\label{sec:benchmarks_description}
In the following, we say {\em both} for an experiment in which we execute both non-vectorized and vectorized protocols and {\em vec} for the vectorized only experiment. 
In a preliminary experiment we ran {\tt N=2, N=4}, all the way to {\tt N=4096}; the non-vectorized version ran out of memory at the value {\em both} and we fixed this value for these experiments. The vectorized one completed for {\tt N=4096} for nearly all benchmarks (numbers are not shown for space reasons).
% however, they times are largely consistent, e.g., if {\em both} is $N = 2^k$ and it completes in $X$ seconds for vectorized, then $N = 2^{12}$ completes in $(12-k)X$ seconds).
We used the following benchmarks in our evaluation:

>>>>

\subsection{Benchmarks}\label{sec:benchmarks_description}

We used benchmarks from ABY and OPA~\cite{NDSS:DemSchZoh15,Ishaq:2019} (Biometric Matching, Histogram, PSI), HyCC~\cite{CCS:BDKKS18} (Database Join, Database Variance, Inner Product, Cryptonets Max Pooling, MNIST ReLU, k-means Iteration) and Parsynth~\cite{Farzan:2021} (Convex Hull, Minimal Points, Count 102, Count 10, Longest 102, Max distance between symbols). 
We did not use Gcd and Modular Exponentiation from~\cite{Ishaq:2019} as they do not benefit from vectorization according to our model. 
We ran as many routines from~\cite{CCS:BDKKS18} and~\cite{Farzan:2021} as possible. Gaussian decomposition cannot be expressed 
in our syntax at the moment and the compiler errors on Cryptonets Convolution at the time of writing, although we expect to fix the issue soon. 
The extended version describes what the benchmarks do in detail~\cite{Anon_TR}.

In the following, we say {\em both} for an experiment in which we execute both non-vectorized and vectorized protocols and {\em vec} for the vectorized only experiment. 
In a preliminary experiment we ran {\tt N=2, N=4}, all the way to {\tt N=4096}; the non-vectorized version ran out of memory at the value for {\em both} and we fixed this value for these experiments. The vectorized one completed for {\tt N=4096} for nearly all benchmarks (numbers are not shown for space reasons).
% however, they times are largely consistent, e.g., if {\em both} is $N = 2^k$ and it completes in $X$ seconds for vectorized, then $N = 2^{12}$ completes in $(12-k)X$ seconds).
